---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 2"
author: "Mahb 2"
date: "10/19/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1 - Denny's in AK

```{r}

dn_ak <- dennys %>% filter(state == "AK")
nrow(dn_ak)

```

### Exercise 2 - La Quinta in AK

```{r}

lq_ak <- laquinta %>% filter(state == "AK") 
nrow(lq_ak)

```

### Exercise 3 - Distance between Denny's and La Quinta in AK

```{r}

dn_lq_ak <- full_join(dn_ak, lq_ak, by = "state") 

```

...

### Exercise 4

```{r}
dn_lq_ak
```

There are 6 observations with 11 variables.
The 11 variables are address (x & y), city(x & y), zip(x & y), longitude(x & y), latitude(x & y), and state.
The x in the variable name is the data from the 'x' data frame which is associated with the Denny's, and 'y' is associated with La Quinta

...

### Exercise 5

```{r}


```

...

### Exercise 6

...

Add exercise headings as needed.
